\ourTitle

### 2022-09-28 paper/manuscript.tex
JPC: Resubmission, cover letter, authors' response and manuscript editted.

\preprint{\arxiv{2206.XXXXX}}

@@

\section{Introduction}
Suppose that we have a finite sequence $x_1 \dots x_L$ of categorical
observations drawn from a temporal process. We may suppose that the process is
stationary (time-translation invariant) and ergodic (explores
all possible behaviors) \cite{Fell70a,Kall01a}. We may wish to forecast from the
observed information the behavior of the next $n$ observations. If we suspect
that the process' temporal correlations do not matter much beyond $k$ symbols,
then we take our data to be all subsequences of length $n+k$,
splitting each subsequence into words of length $k$ and $n$ respectively. From
these ``past/future'' pairs we can construct an empirical conditional
distribution
\begin{align*}
  \widehat{P}_{x_{1}\dots x_{n}|x_{-k+1}\dots x_0} = 
  \frac{C_{x_{-k+1}\dots x_{n}}}{C_{x_{-k+1}\dots x_0}}
  ~,
\end{align*}
where $C_{w}$ is the number of times the word $w$ appears in our sequence $x_1
\dots x_L$.

@@

Examples 3 through 5, in particular, involve long-range
correlations in their sequences which arise from structures which, upon
``opening,'' must be ``closed'' an arbitrary time later. Such structures are
present in human language as well as in genetic sequences. In the latter case,
this long-range correlation exists due to the folding of proteins which allows
distant codons to interact with one another. Detecting and modeling these
folding structures requires
more complex models than hidden Markov models, such as the context-free grammars
in examples 3 and 4 \cite{Saka94a}. 
Example 6 represents the general problem of recovering knowledge of a dynamical
system of which only coarse-grained data is available.

>>>>

\preprint{\arxiv{2206.04198}}

@@

\section{Introduction}
Suppose that we have a finite sequence $x_1 \dots x_L$ of categorical
observations drawn from a temporal process. We may suppose that the process is
stationary (time-translation invariant) and ergodic (explores
all possible behaviors) \cite{Fell70a,Kall01a}. We may wish to forecast from the
observed information the behavior of the next $n$ observations. If we suspect
that the process' temporal correlations do not matter much beyond $k$ symbols,
then we take our data to be all subsequences of length $n+k$,
splitting each subsequence into words of length $k$ and $n$, respectively. From
these ``past/future'' pairs we can construct an empirical conditional
distribution
\begin{align*}
  \widehat{P}_{x_{1}\dots x_{n}|x_{-k+1}\dots x_0} = 
  \frac{C_{x_{-k+1}\dots x_{n}}}{C_{x_{-k+1}\dots x_0}}
  ~,
\end{align*}
where $C_{w}$ is the number of times the word $w$ appears in our sequence $x_1
\dots x_L$.

@@

Examples 3 through 5, in particular, involve long-range
correlations in their sequences that arise from structures which, upon
``opening,'' must be ``closed'' an arbitrary time later. Such structures are
present in human language as well as in genetic sequences. In the latter case,
this long-range correlation exists due to the folding of proteins which allows
distant codons to interact with one another. Detecting and modeling these
folding structures requires
more complex models than hidden Markov models, such as the context-free grammars
in examples 3 and 4 \cite{Saka94a}. 
Example 6 represents the general problem of recovering knowledge of a dynamical
system of which only coarse-grained data is available.
